Analyzing opportunities arround city traffic optimization

### 2020-01-19 thesis/report1.tex
Referral 1: few more words on the hot areas analyzer.

Hot areas are defined as places or streets where traffic is pilling up more than in other areas. Intuitively

>>>>

Hot areas are defined as places or streets where traffic is pilling up more than in other areas. Figure \ref{fig:ScreenshotWebInterface2} \citep{microservicestrafficsimulation} shows such a analyze using visual cues: streets are colored with red where there cars on them. A slight implementation of this would be to color them gradually and proportional with how many cars are on a specific street. Therefore the human eye will have a better understanding. Other places which could be analyzed are junctions. Figure \ref{fig:ScreenshotWebInterface2} doesn't show how much load are on junctions or roundabouts but there is an opportunity to take adjacent numbers from the city simulator and compute how much cars are able to pass a certain junction.
